Single-step Hybrid Predition

### 2016-12-07 reports/single_step_kernels.Rmd
Match names of original to names of transformed kernels

# Kernel Inspection
```{r setup-kernel-inspection, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
if (!require("devtools")) install.packages("devtools")
devtools::install_github("mwesthues/sspredr", update = TRUE)
pacman::p_load("BGLR","data.table", "tidyverse", "dtplyr", "caret", "e1071")
pacman::p_load_gh("mwesthues/sspredr")

@@

# As a requirement of the kernel-generating functions, add the names of the 
# hybrid parents to each predictor-set/group combination.
cat_lst <- lapply(seq_along(feat_lst), FUN = function(i) {
  x_lvl1 <- feat_lst[[i]] 
  y_lvl1 <- hybrid_parent_nms[[i]]
  geno_lst <- lapply(seq_along(x_lvl1), FUN = function(j) {
    x_lvl2 <- x_lvl1[[j]]
    y_lvl2 <- y_lvl1[[j]]
    x_lvl2[["geno"]] <- y_lvl2
    x_lvl2
  })
  names(geno_lst) <- names(x_lvl1)
  geno_lst
})
saveRDS(cat_lst,
        file = "./data/derived/pred_sub_list.RDS")

@@

snp100_mrna42_none <- cat_lst %>%
  transpose() %>%
  .[["snp100_mrna42_none"]] %>%
  map(~impute_eta(
     x = .[[1]],
     y = .[[2]],
     geno = .[["geno"]],
     as_kernel = TRUE,
     is_pedigree = FALSE,
     bglr_model = "BRR"
    )
  ) %>%
  map(2) %>%
  map("X")

ped100_x_none <- cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("ped100_mrna42_none", "ped100_snp77_none")] %>%
  at_depth(.depth = 2, .f = ~impute_eta(
    x = .[[1]],
    y = .[[2]],
    geno = .[["geno"]], 
    as_kernel = TRUE,
    is_pedigree = TRUE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 2) %>%
  at_depth(.depth = 2, .f = "X")

pedx_none_none <- cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("ped100_none_none", "ped42_none_none")] %>%
  at_depth(.depth = 2, .f = ~complete_eta(
    x = .[[1]],
    geno = .[["geno"]],
    as_kernel = FALSE,
    is_pedigree = TRUE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 1) %>%
  at_depth(.depth = 2, .f = "X")

single_pred <- cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("snp42_none_none", "mrna42_none_none", 
                    "snp100_none_none")] %>%
  at_depth(.depth = 2, .f = ~complete_eta(
    x = .[[1]],
    geno = .[["geno"]],
    as_kernel = TRUE,
    is_pedigree = FALSE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 1) %>%
  at_depth(.depth = 2, .f = "X")

# Combine the results in a single list to reduce code replications (the
# following steps are the same for all predictor sets).
W_lst <- c(list(ped100_snp77_mrna42 = ped100_snp77_mrna42),
           list(snp100_mrna42_none = snp100_mrna42_none),
           pedx_none_none,
           ped100_x_none,
           single_pred)
```

>>>>

# Kernel Inspection
```{r setup-kernel-inspection, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
if (!require("devtools")) install.packages("devtools")
devtools::install_github("mwesthues/sspredr", update = TRUE)
pacman::p_load("BGLR","data.table", "tidyverse", "dtplyr", "caret", "e1071",
               "stringr")
pacman::p_load_gh("mwesthues/sspredr")

@@

# As a requirement of the kernel-generating functions, add the names of the 
# hybrid parents to each predictor-set/group combination.
cat_lst <- lapply(seq_along(feat_lst), FUN = function(i) {
  x_lvl1 <- feat_lst[[i]] 
  y_lvl1 <- hybrid_parent_nms[[i]]
  geno_lst <- lapply(seq_along(x_lvl1), FUN = function(j) {
    x_lvl2 <- x_lvl1[[j]]
    y_lvl2 <- y_lvl1[[j]]
    x_lvl2[["geno"]] <- y_lvl2
    x_lvl2
  })
  names(geno_lst) <- names(x_lvl1)
  geno_lst
})
names(cat_lst) <- names(feat_lst)

# Remove empty names (i.e. 'none') from predictor set names.
cat_lst <- cat_lst %>%
  map(function(x) {
    names(x) <- str_replace_all(names(x), pattern = "_none", replacement = "")
    x
  })
saveRDS(cat_lst,
        file = "./data/derived/pred_sub_list.RDS")

@@

snp100_mrna42 <- cat_lst %>%
  transpose() %>%
  .[["snp100_mrna42"]] %>%
  map(~impute_eta(
     x = .[[1]],
     y = .[[2]],
     geno = .[["geno"]],
     as_kernel = TRUE,
     is_pedigree = FALSE,
     bglr_model = "BRR"
    )
  ) %>%
  map(2) %>%
  map("X")

ped100_x <- cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("ped100_mrna42", "ped100_snp77")] %>%
  at_depth(.depth = 2, .f = ~impute_eta(
    x = .[[1]],
    y = .[[2]],
    geno = .[["geno"]], 
    as_kernel = TRUE,
    is_pedigree = TRUE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 2) %>%
  at_depth(.depth = 2, .f = "X")

pedx <- cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("ped100", "ped42")] %>%
  at_depth(.depth = 2, .f = ~complete_eta(
    x = .[[1]],
    geno = .[["geno"]],
    as_kernel = FALSE,
    is_pedigree = TRUE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 1) %>%
  at_depth(.depth = 2, .f = "X")

single_pred <- cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("snp42", "mrna42", "snp100")] %>%
  at_depth(.depth = 2, .f = ~complete_eta(
    x = .[[1]],
    geno = .[["geno"]],
    as_kernel = TRUE,
    is_pedigree = FALSE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 1) %>%
  at_depth(.depth = 2, .f = "X")

# Combine the results in a single list to reduce code replications (the
# following steps are the same for all predictor sets).
W_lst <- c(list(ped100_snp77_mrna42 = ped100_snp77_mrna42),
           list(snp100_mrna42 = snp100_mrna42),
           pedx,
           ped100_x,
           single_pred)
```

### 2016-12-07 reports/transformed_kernels.Rmd
Match names of original to names of transformed kernels

# Remove perfect LD
snp42 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "snp42_none_none"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

snp77 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped100_snp77_none"] %>%
  at_depth(.depth = 2, .f = 2) %>%
  .[[1]]

snp100 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "snp100_none_none"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

@@

# Get pedigree data
ped100 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped100_snp77_none"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped100) <- c("Dent", "Flint")

ped42 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped42_none_none"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped42) <- c("Dent", "Flint")
```

```{r Kernel-assembly, cache = TRUE}
nms100 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "ped100_none_none"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

nms42 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "mrna42_none_none"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

# Specify the predictor sets.
pred_vec <- c("snp42-none-none", "mrna42-none-none", "snp100-none-none",
              "ped100-snp77-none", "ped100-mrna42-none", "snp100-mrna42-none",
              "ped100-snp77-mrna42")
pred_sets <- pred_vec %>%
  strsplit(., split = "[-]") %>%
  map(.f = function(x) {
    x[x != "none"] 
  })

>>>>

# Remove perfect LD
snp42 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "snp42"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

snp77 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped100_snp77"] %>%
  at_depth(.depth = 2, .f = 2) %>%
  .[[1]]

snp100 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "snp100"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

@@

# Get pedigree data
ped100 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped100_snp77"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped100) <- c("Dent", "Flint")

ped42 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped42"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped42) <- c("Dent", "Flint")
```

```{r Kernel-assembly, cache = TRUE}
nms100 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "ped100"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

nms42 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "mrna42"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

# Specify the predictor sets.
pred_sets <- c(
  "snp42", "mrna42", "snp100", "ped100-snp77", "ped100-mrna42",
  "snp100-mrna42", "ped100-snp77-mrna42"
  ) %>%
  strsplit(., split = "[-]")
